Democracy, Public Support, and Measurement Uncertainty

### 2021-08-11 paper/dcpo_demsupport.Rmd
add DCPO in SI.

load(here("data","claassen_replication_input.rda"))
load(here("data","exp_claassen_input.rda"))

@@

mocresult_correctAJPS <- readRDS(here("output", "estimates_moc_correctAJPS.RDS")) 
mocresult_expAJPS <- readRDS(here("output", "estimates_moc_expcorAJPS.RDS"))
mocresult_correctAPSR <- readRDS(here("output", "estimates_moc_correctAPSR.RDS"))
mocresult_expAPSR <- readRDS(here("output", "estimates_moc_expcorAPSR.RDS"))

@@

supdem_ncy <- supdem %>%
  dplyr::select(country, year) %>% 
  distinct() %>% 
  nrow()

@@

Specifically, we are not able to identify 5 cournty-year surveys, including South Sudan in Arab Barometer Wave 4, Dominican Republic in 2003 Latinobarometer, XXXX, and Spain in 2005 Latinobarometer. 
In addition, we still have different sample size and number of respondents answering supportively by following approaches of cleanning data and treatment of non-responses described in @Claassen2020a's supplementatry materials.
Specifically, we used Claassen's year coding to recode 85 unmatching country-year observations and added one more item "strong leader 2" in Arabbarometer which has different response categories but was conflated into "strong leader 1".

@@

@@

In analysis models, we have latent variables in both sides of equations, public suppport for democracy, democracy indices and corruption index (The latter one is included in APSR analyses).
Since measurement uncertainty associated with these latent variables can propogate into the inferences over coefficient parameters in models, we incorporate uncertainty by employing "Method of Composition" [@Tanner1996,p52], which has been applied in analyses with latent variables [@Treier2008;@Caughey2018;@Kastellec2015].

As @Caughey2018 explained, the main idea of MOC is to estimate the marginal distribution of coefficient parameter vector $\beta$, intergrating over the uncertainty in latent variables $\theta$ (P A-15).
More explicitly, we wish to integrate the joint density of $\beta$ and $\theta$ over the distribution of $\theta$.

@@

where $\theta$ is latent varibles with measurement errors conditional on data Z and a measurement model, $w$ is other predictors without errors, $Z$ is indicators for latent variables $X$, and $y$ is the outcome variable.
In this way, we incorportate uncertainty in measuring predictor $\theta$, and uncertainty in the effects of latent variables $\theta$ and other variables $w$ on outcome variable $y$ [@Treie2008, 215].
To sample from the conditional dentsity and the marginal density in the right side of the equation, we follow iterative Monte Carlo procdure described by @Treier2008, at iteration t,
1. We sample $\theta^{s}$ from its posterior distribution $p(\theta|Z)$ and $y$ from $p(y|Z)$. 
2. For each analysis model, we run the model with $y$, $\theta$, and $w$, and save the coefficient estimates $\beta^{s}$ and variance-covariance matrix of $\beta^{s}$, $V^{s}$, both of which change due to the uncertainty in $\theta^{s}$ and $y^{s}$.
3. We sample $\tilde{\beta^{t}}$ from the multivariate normal density with mean vector $\beta{s}$ and variance-covariace matrix $V^{s}$.

>>>>

load(here("data","claassen_replication_input.rda"))
load(here("data","exp_claassen_input.rda"))
load(here("data","dcpo_apsr.rda"))
load(here("data","dcpo_ajps.rda"))

@@

result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
result_clsAJPS <- readRDS(here("output", "estimates_clsMeanAJPS.RDS"))

mocresult_correctAJPS <- readRDS(here("output", "estimates_moc_correctAJPS.RDS")) 
mocresult_expAJPS <- readRDS(here("output", "estimates_moc_expcorAJPS.RDS"))
mocresult_correctAPSR <- readRDS(here("output", "estimates_moc_correctAPSR.RDS"))
mocresult_expAPSR <- readRDS(here("output", "estimates_moc_expcorAPSR.RDS"))
mocdcpo_APSR <- readRDS(here("ouput","estimates_moc_dcpoAPSR.RDS"))
mocresult_dcpoAJPS <- readRDS(here("output","estimates_moc_dcpoAJPS.RDS"))
```

@@

supdem_ncy <- supdem %>%
  dplyr::select(country, year) %>% 
  distinct() %>% 
  nrow() #1165

@@

Specifically, we are not able to identify 5 country-year surveys, including South Sudan in Arab Barometer Wave 4, Dominican Republic in 2003 Latinobarometer, XXXX, and Spain in 2005 Latinobarometer. 
In addition, we still have different sample size and number of respondents answering supportively by following approaches of cleanning data and treatment of non-responses described in @Claassen2020a's supplementatry materials.
Specifically, we used Claassen's year coding to recode 85 unmatching country-year observations and added one more item "strong leader 2" in Arabbarometer which has different response categories but was conflated into "strong leader 1".

@@

# DCPO Replication {#dcpo}

```{r dcpo-APSR, eval=FALSE}

dcpo_APSR <- purrr::map(1:900, function(anEntry) {
  dcpo_apsr[[anEntry]] %>% 
    plm::pdata.frame(index = c("country", "year")) %>%
    rename(SupDem_trim = theta_trim,
          First_yr = first_year,
          Libdem_z = Vdem_libdem_z,
          Polyarchy_z = Vdem_polyarchy_z,
          Liberal_z = Vdem_liberal_z,
          Corrup_TI_z = corruption_z,
          lnGDP_imp = lg_imp_mdpgdp)
}
)

mocdcpo_APSR  <- map(ls_mod_apsrCLS, function(aMod){
  result <- methodComposition3(dcpo_APSR,aMod)
})

names(mocdcpo_APSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",
                                "fd1", "fd-regime1", "fd2", "fd-regime2")

saveRDS(mocdcpo_APSR, file = here::here("ouput","estimates_moc_dcpoAPSR.RDS"))
```

```{r formatDCPOResult-APSR}
# Pooled---------------------------------------

result_ecm1 <- bind_rows(
  mutate(result_clsAPSR[["pooled1"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_expAPSR[["pooled1"]]), model = "Uncertianty+ExpData"),
  mutate(MOCsumm2(mocdcpo_APSR[["pooled1"]]), model = "Uncertianty+DCPO+ExpData")
) %>% 
  mutate(type = "ECM")

result_fd1 <- bind_rows(
  mutate(result_clsAPSR[["fd1"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_expAPSR[["fd1"]]), model = "Uncertianty+ExpData"),
  mutate(MOCsumm2(mocdcpo_APSR[["fd1"]]), model = "Uncertianty+DCPO+ExpData")
) %>% 
  mutate(type = "First Difference")

result_APSR1 <- bind_rows(result_ecm1, result_fd1) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
        "Liberal Democracy\n (Difference)",
        "Liberal Democracy\n (t-1)",
        "Log GDP\n per capita\n (Difference)",
        "Log GDP\n (t-1)"),
      time = 3),
      rep(
        c("Liberal Democracy\n (Difference)", 
          "Log GDP\n per capita\n (Difference)"), 
        time = 3
      )),
    type = factor(type,  levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Original","Uncertianty+ExpData", "Uncertianty+DCPO+ExpData"))
  )

result_ecmReg1 <- bind_rows(
  mutate(result_clsAPSR[["pooled-regime1"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime1"]]), model = "Uncertianty+ExpData"),
  mutate(MOCsumm2(mocdcpo_APSR[["pooled-regime1"]]), model = "Uncertianty+DCPO+ExpData")
) %>% 
  mutate(type = "ECM")

result_fdReg1 <- bind_rows(
  mutate(result_clsAPSR[["fd-regime1"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_expAPSR[["fd-regime1"]]), model = "Uncertianty+ExpData"),
  mutate(MOCsumm2(mocdcpo_APSR[["fd-regime1"]]), model = "Uncertianty+DCPO+ExpData")
) %>% 
  mutate(type = "First Difference")

result_RegAPSR1 <- bind_rows(result_ecmReg1, result_fdReg1) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
        "Electoral Democracy\n (Difference)",
        "Electoral Democracy\n (t-1)",
        "Minoritarian Democracy\n (Difference)",
        "Minoritarian Democracy\n (t-1)",
        "Log GDP\n per capita\n (Difference)",
        "Log GDP\n (t-1)"),
      time = 3),
      rep(
        c("Electoral Democracy\n (Difference)", 
          "Minoritarian Democracy\n (Difference)",
          "Log GDP\n per capita\n (Difference)"), 
        time = 3
      )),
    type = factor(type,  levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Original","Uncertianty+ExpData", "Uncertianty+DCPO+ExpData"))
  )

result_ecm2 <- bind_rows(
  mutate(result_clsAPSR[["pooled2"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_expAPSR[["pooled2"]]), model = "Uncertianty+ExpData"),
  mutate(MOCsumm2(mocdcpo_APSR[["pooled2"]]), model = "Uncertianty+DCPO+ExpData")
) %>% 
  mutate(type = "ECM")

result_fd2 <- bind_rows(
  mutate(result_clsAPSR[["fd2"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_expAPSR[["fd2"]]), model = "Uncertianty+ExpData"),
  mutate(MOCsumm2(mocdcpo_APSR[["fd2"]]), model = "Uncertianty+DCPO+ExpData")
) %>% 
  mutate(type = "First Difference")

result_APSR2 <- bind_rows(result_ecm2, result_fd2) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
        "Liberal Democracy\n (Difference)",
        "Liberal Democracy\n (t-1)",
        "Log GDP\n per capita\n (Difference)",
        "Log GDP\n (t-1)",
        "Corruption\n (Difference)",
        "Corruption\n (t-1)"
      ),
      time = 3),
      rep(
        c("Liberal Democracy\n (Difference)", 
          "Log GDP\n per capita\n (Difference)",
          "Corruption\n (Difference)"), 
        time = 3
      )),
    type = factor(type,  levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Original","Uncertianty+ExpData", "Uncertianty+DCPO+ExpData"))
  )

result_ecmReg2 <- bind_rows(
  mutate(result_clsAPSR[["pooled-regime2"]][[1]][,1:3], model = "Original"),
 mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime2"]]), model = "Uncertianty+ExpData"),
  mutate(MOCsumm2(mocdcpo_APSR[["pooled-regime2"]]), model = "Uncertianty+DCPO+ExpData")) %>%
  mutate(type = "ECM")

result_fdReg2 <- bind_rows(
  mutate(result_clsAPSR[["fd-regime2"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_expAPSR[["fd-regime2"]]), model = "Uncertianty+ExpData"),
  mutate(MOCsumm2(mocdcpo_APSR[["fd-regime2"]]), model = "Uncertianty+DCPO+ExpData")) %>% 
  mutate(type = "First Difference")

result_RegAPSR2 <- bind_rows(result_ecmReg2, result_fdReg2) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
        "Electoral Democracy\n (Difference)",
        "Electoral Democracy\n (t-1)",
        "Minoritarian Democracy\n (Difference)",
        "Minoritarian Democracy\n (t-1)",
        "Log GDP\n per capita\n (Difference)",
        "Log GDP\n (t-1)",
        "Corruption\n (Difference)",
        "Corruption\n (t-1)"
      ),
      time = 3),
      rep(
        c("Electoral Democracy\n (Difference)", 
          "Minoritarian Democracy\n (Difference)",
          "Log GDP\n per capita\n (Difference)",
          "Corruption\n (Difference)"), 
        time = 3
      )),
    type = factor(type,  levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Original","Uncertianty+ExpData", "Uncertianty+DCPO+ExpData"))
  )
```

```{r plot-mainDCPOAPSR, fig.cap= "The Effect of Democracy on the Change of Public Support", fig.width=7, fig.height=10}
type_model <-
    c("Original", "Uncertianty+ExpData", "Uncertianty+DCPO+ExpData")

```{r moc-dcpoAJPS, eval=FALSE}

dcpo_Ajps <- purrr::map(1:900, function(anEntry) {
  dcpo_ajps[[anEntry]] %>% 
    plm::pdata.frame(index = c("country", "year")) %>%
    rename(SupDem_trim =theta_trim,
           Regime_VD = Vdem_regime,
           Pr_Muslim = muslism_prop_2010,
           Res_cp_WDI_di = dependence_pc_di,
           lnGDP_imp = lg_imp_mdpgdp,
           GDP_imp_grth = mdprgdp_grwth,
           firstyear = first_year,
           Libdem_VD = Vdem_libdem,
           Libdem_m1 = Vdem_libdem_m1,
           Libdem_m2 = Vdem_libdem_m2,
           ChgDem = Chgdem,
           UpChgDem = upchgdem,
           DwnChgDem = downchgdem,
           Libdem_regUN = Region_libdem,
           Libdem_regUN_m1 = Region_libdem_m1)
})

result_dcpoUncertain  <- map(ls_mod_ajpsCLS[1:2], function(aMod){
  result <- methodComposition1(dcpo_Ajps,aMod)
})

names(result_dcpoUncertain) <- c("pooled", "pooled-regime")

result_dcpoUncertain_gmm  <- map(ls_mod_ajpsCLS[3:4], function(aMod){
  result <- methodComposition2(dcpo_Ajps,aMod)
})
names(result_dcpoUncertain_gmm) <- c("gmm", "gmm-regime")

mocresult_dcpoAJPS <- append(result_dcpoUncertain, result_dcpoUncertain_gmm)
saveRDS(mocresult_dcpoAJPS, file =here("output","estimates_moc_dcpoAJPS.RDS"))

```{r formatDCPOResult-AJPS}
result_pooled <- bind_rows(
  mutate(result_clsAJPS[["pooled"]][[1]][,1:3], model = "Original"),
 mutate(MOCsumm(mocresult_expAJPS[["pooled"]]), model = "Uncertianty+ExpData"),
 mutate(MOCsumm(mocresult_dcpoAJPS[["pooled"]]), model = "Uncertianty+DCPO+ExpData")
) %>% 
  mutate(type = "Pooled")

result_gmm <- bind_rows(
  mutate(result_clsAJPS[["gmm"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm(mocresult_expAJPS[["gmm"]]), model = "Uncertianty+ExpData"),
  mutate(MOCsumm(mocresult_dcpoAJPS[["gmm"]]), model = "Uncertianty+DCPO+ExpData")
) %>% 
  mutate(type = "GMM")

result_pooledAJPS <- bind_rows(result_pooled, result_gmm) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democracy\n (t-1)",
        "Democracy\n (t-2)",
        "Support\n (t-1)",
        "Log GDP\n per capita\n (t-1)",
        "GDP per\n capita growth\n (t-1)",
        "Regional\n democracy\n (t-1)",
        "Percent\n Muslim\n (t-1)",
        "Resource\n dependence\n (t-1)"),
      time = 6), 
    type = factor(type, levels = c("Pooled", "GMM")),
    model = factor(model, levels = c("Original", "Uncertianty+ExpData", "Uncertianty+DCPO+ExpData")))

result_regime <- bind_rows(
  mutate(result_clsAJPS[["pooled-regime"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm(mocresult_expAJPS[["pooled-regime"]]), model = "Uncertianty+ExpData"),
  mutate(MOCsumm(mocresult_dcpoAJPS[["pooled-regime"]]), model = "Uncertianty+DCPO+ExpData")
) %>% 
  mutate(type = "Pooled")

result_regimeGmm <- bind_rows(
  mutate(result_clsAJPS[["gmm-regime"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm(mocresult_expAJPS[["gmm-regime"]]), model = "Uncertianty+ExpData"),
 mutate(MOCsumm(mocresult_dcpoAJPS[["gmm-regime"]]), model = "Uncertianty+DCPO+ExpData")
)%>% 
  mutate(type = "GMM")

result_regimeAJPS <- bind_rows(result_regime, result_regimeGmm) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democracy\n (t-1)",
        "Democracy\n (t-2)",
        "Support\n demo only\n (t-1)",
        "Support\n auto only\n (t-1)",
        "Log GDP\n per capita\n (t-1)",
        "GDP per\n capita growth\n (t-1)",
        "Regional\n democracy\n (t-1)",
        "Percent\n Muslim\n (t-1)",
        "Resource\n dependence\n (t-1)"),
      time = 6), 
    type = factor(type, levels = c("Pooled", "GMM")),
    model = factor(model, levels = c("Original","Uncertianty+ExpData", "Uncertianty+DCPO+ExpData")))

```{r plotdcpo-mainAJPS, fig.cap= "The Effect of Public Support on Democracy with Uncertainty", fig.width=7, fig.height=10, fig.align='center'}

type_model <-
  c("Original", "Uncertianty+ExpData", "Uncertianty+DCPO+ExpData")

@@

In analysis models, we have latent variables in both sides of equations, public suppport for democracy, democracy indices and corruption index (The latter one is included in APSR analyses).
Since measurement uncertainty associated with these latent variables can propogate into the inferences over coefficient parameters in models, we incorporate uncertainty by employing "Method of Composition" [@Tanner1996,p52], which has been applied in analyses with latent variables [@treier2008;@caughey2018;@Kastellec2015].

As @caughey2018 explained, the main idea of MOC is to estimate the marginal distribution of coefficient parameter vector $\beta$, intergrating over the uncertainty in latent variables $\theta$ (P A-15).
More explicitly, we wish to integrate the joint density of $\beta$ and $\theta$ over the distribution of $\theta$.

@@

where $\theta$ is latent varibles with measurement errors conditional on data Z and a measurement model, $w$ is other predictors without errors, $Z$ is indicators for latent variables $X$, and $y$ is the outcome variable.
In this way, we incorportate uncertainty in measuring predictor $\theta$, and uncertainty in the effects of latent variables $\theta$ and other variables $w$ on outcome variable $y$ [@treie2008, 215].
To sample from the conditional dentsity and the marginal density in the right side of the equation, we follow iterative Monte Carlo procdure described by @Treier2008, at iteration t,
1. We sample $\theta^{s}$ from its posterior distribution $p(\theta|Z)$ and $y$ from $p(y|Z)$. 
2. For each analysis model, we run the model with $y$, $\theta$, and $w$, and save the coefficient estimates $\beta^{s}$ and variance-covariance matrix of $\beta^{s}$, $V^{s}$, both of which change due to the uncertainty in $\theta^{s}$ and $y^{s}$.
3. We sample $\tilde{\beta^{t}}$ from the multivariate normal density with mean vector $\beta{s}$ and variance-covariace matrix $V^{s}$.
